SVG: The Paper

### 2022-05-03 Analysis/index.Rmd
editing figure

```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model. (*right*) The proportion of trials the item with the largest assigned weight was selected by the participant.  Each dot shows data from an individual particpant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}

@@

ggsave("../Figures/qjep_preds.png", width = 8, height = 4)

@@

@@

ggplot(a_cut, aes(b_bin, acc, colour = condition, shape = condition)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("largest item weight") +
  scale_y_continuous("proportion of times selected") +
  theme(legend.position = "bottom") -> plt1

@@

plt1 + plt2
```

>>>>

```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model. (*right*) The proportion of trials the item with the largest assigned weight was selected by the participant.  Each dot shows data from an individual participant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}

@@

@@

rm(plt_c)

@@

ggplot(a_cut, aes(b_bin, acc, colour = condition, fill = condition, shape = condition)) + 
  geom_point() + 
  geom_line(stat = "smooth", method = "loess", 
            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
  geom_abline(linetype = 2) +
  scale_x_continuous("largest item weight") +
  scale_y_continuous("proportion of times selected") +
  theme(legend.position = "bottom") -> plt1

@@

 plt1 + plt2

ggsave("../Figures/qjep_preds.png", 
       plt_b + plt1 + plt2 + plot_layout(guides = "collect") & theme(legend.position = "bottom"),
       width = 10, height = 4)
